A framework for adaptive width control of dense contour-parallel toolpaths in \revise{additive manufacturing}{fused deposition modeling}

### 2020-01-20 0_main.tex
fix double References header
new revise macros
new revision command
reenable temp commands in main
fix pdfedlink bug (from hyperref package)
change department name
add censoring (for reproduction in apendix of INRIA paper)

@@

%    \newcommand{\todo}[1]{\hl{#1}}
%    
%	\newcommand{\temp}[1]{\textcolor[rgb]{0, 0, 0.2}{#1}}
%	\newcommand{\tim}[1]{\temp{\todo{[Tim: #1]}}}
%	\newcommand{\jun}[1]{\temp{\todo{[Jun: #1]}}}
%	
%	\newcommand{\old}[1]{\textcolor{gray}{#1}}
	\usepackage[normalem]{ulem}
	\newcommand{\stkout}[1]{\ifmmode\text{\sout{\ensuremath{#1}}}\else\sout{#1}\fi}

	% Revise macro (usage: \revise{old}{new})
	% Version a) First arg red and striked out, second argument green
	\newcommand{\revise}[2]{\textcolor{red}{\stkout{#1}}\textcolor{blue}{#2}}
	% Version b) First arg ignored, second argument green
	%\newcommand{\revise}[2]{\textcolor{blue}{#2}}
	% Version c) First arg ignored, second argument unchanged (for final draft)
	%\newcommand{\revise}[2]{#2}

@@

\author[um,tud]{Tim Kuipers}
\author[tud]{Eugeni L. Doubrovski}
\author[tud]{Jun Wu\corref{cor1}}
\ead{j.wu-1@tudelft.nl}
\cortext[cor1]{Corresponding author}
\author[cuhk]{Charlie Wang}
% \ead{cwang@mae.cuhk.edu.hk}
\address[um]{Ultimaker, Utrecht, The Netherlands}
\address[tud]{Department of Design Engineering, Delft University of Technology, The Netherlands}
\address[cuhk]{Department of Mechanical and Automation Engineering, The Chinese University of Hong Kong, Hong Kong SAR, China}

@@

\section*{References}
\bibliography{99_mybib}

>>>>

    \usepackage{censor}
	\def\censorcolor{black}
	\let\svcensorrule\censorrule
	\renewcommand\censorrule[1]{%
	\textcolor{\censorcolor}{\svcensorrule{#1}}}

	\newcommand{\censoromit}[1]{}
	%\newcommand{\censoromit}[1]{#1}
    % \StopCensoring

@@

    \newcommand{\todo}[1]{\hl{#1}}

	\newcommand{\temp}[1]{\textcolor[rgb]{0, 0, 0.2}{#1}}
	\newcommand{\tim}[1]{\temp{\todo{[Tim: #1]}}}
	\newcommand{\jun}[1]{\temp{\todo{[Jun: #1]}}}

	\newcommand{\old}[1]{\textcolor{gray}{#1}}
	\usepackage[normalem]{ulem}
	\newcommand{\stkout}[1]{\ifmmode\text{\sout{\ensuremath{#1}}}\else\sout{#1}\fi}

	% Revise macro (usage: \revise{old}{new})
	% Version a) First arg red and striked out, second argument green
	%\newcommand{\revise}[2]{\textcolor{red}{\stkout{#1}}\textcolor{blue}{#2}}
	%\newcommand{\revise}[2]{{\color{red}{#1}\color{blue}{#2}}}
	% Version b) First arg ignored, second argument green
	\newcommand{\revise}[2]{{\color{blue}{#2}}}
	% Version c) First arg ignored, second argument unchanged (for final draft)
	%\newcommand{\revise}[2]{#2}
	%\newcommand{\revise}[2]{#1}

@@

\author[um,tud]{\censor{Tim Kuipers}}
\author[tud]{\censor{Eugeni L. Doubrovski}}
\author[tud]{\censor{Jun Wu}\corref{cor1}}
\censoromit{\ead{j.wu-1@tudelft.nl}}
\cortext[cor1]{Corresponding author}
\author[cuhk]{\censor{Charlie Wang}}
% \ead{cwang@mae.cuhk.edu.hk}
\address[um]{\censor{Ultimaker, Utrecht, The Netherlands}}
\address[tud]{\censor{Department of Sustainable Design Engineering, Delft University of Technology, The Netherlands}}
\address[cuhk]{\censor{Department of Mechanical and Automation Engineering, The Chinese University of Hong Kong, Hong Kong SAR, China}}

@@

%\section*{References}
\interlinepenalty=100000 % prevents pdfendlink ended up accross pages error. see https://tex.stackexchange.com/a/449633/129190
\bibliography{99_mybib}

### 2020-01-20 10_applications.tex
add censoring (for reproduction in apendix of INRIA paper)

\begin{figure*}
\centering
\setlength{\figwidth}{0.099\textwidth}
\setlength{\figheight}{0.099\textwidth}
\begin{subfigure}{\textwidth}\centering
\includegraphics[width=\textwidth]{sources-applications-combined-small-dilated-circled.pdf}
%\caption{Overview}\label{applications_overview}
\end{subfigure}
\begin{subfigure}[t]{\figwidth}\centering
\includegraphics[height=\figheight]{sources-applications-house.png}
\caption{House}\label{applications_house}
\end{subfigure}
\begin{subfigure}[t]{\figwidth}\centering
\includegraphics[height=\figheight]{sources-applications-pocket-operator-case.png}
\caption{Case}\label{applications_case}
\end{subfigure}
\begin{subfigure}[t]{\figwidth}\centering
\includegraphics[height=\figheight]{sources-applications-david.png}
\caption{Statue}\label{applications_statue}
\end{subfigure}
\begin{subfigure}[t]{\figwidth}\centering
\includegraphics[height=\figheight]{sources-applications-tud-logo.png}
\caption{TUD}\label{applications_tud}
\end{subfigure}
\begin{subfigure}[t]{\figwidth}\centering
\includegraphics[height=\figheight]{sources-applications-ultimaker-logo.png}
\caption{UM}\label{applications_um}
\end{subfigure}
\begin{subfigure}[t]{\figwidth}\centering
\includegraphics[height=\figheight]{sources-applications-pinion-gear-motor.png}
\caption{Gear}\label{applications_gear}
\end{subfigure}
\begin{subfigure}[t]{\figwidth}\centering
\includegraphics[height=\figheight]{sources-applications-topopt-bone.png}
\caption{Bone}\label{applications_bone}
\end{subfigure}
\begin{subfigure}[t]{\figwidth}\centering
\includegraphics[height=\figheight]{sources-applications-gyroid.png}
\caption{Gyroid}\label{applications_gyroid}
\end{subfigure}
\begin{subfigure}[t]{\figwidth}\centering
\includegraphics[height=\figheight]{sources-applications-hex-grid.png}
\caption{Hex}\label{applications_hex}
\end{subfigure}
\begin{subfigure}[t]{.3\figwidth}
\includegraphics[height=\figheight]{sources-validation-widths-legend-small.pdf}
\end{subfigure}
\caption{
Visualization of the widths for the output toolpaths of the inward distributed beading scheme \revise{}{($N=3$) }applied to various example application objects.
From left to right and top to bottom: a house, a case for electronics, a statue, two common logos, a gear, a topologically optimized bone structure, a tilted homogeneous gyroid structure and a heterogeneous thickness hexagonal grid.
}
\label{applications_overview}
\end{figure*}

>>>>

\begin{figure*}
\centering
\setlength{\figwidth}{0.099\textwidth}
\setlength{\figheight}{0.099\textwidth}
\begin{subfigure}{\textwidth}\centering
\censorbox{
\includegraphics[width=\textwidth]{sources-applications-combined-small-dilated-circled.pdf}
}
%\caption{Overview}\label{applications_overview}
\end{subfigure}
\begin{subfigure}[t]{\figwidth}\centering
\includegraphics[height=\figheight]{sources-applications-house.png}
\caption{House}\label{applications_house}
\end{subfigure}
\begin{subfigure}[t]{\figwidth}\centering
\includegraphics[height=\figheight]{sources-applications-pocket-operator-case.png}
\caption{Case}\label{applications_case}
\end{subfigure}
\begin{subfigure}[t]{\figwidth}\centering
\includegraphics[height=\figheight]{sources-applications-david.png}
\caption{Statue}\label{applications_statue}
\end{subfigure}
\begin{subfigure}[t]{\figwidth}\centering
\censorbox{
\includegraphics[height=\figheight]{sources-applications-tud-logo.png}
}
\caption{\censor{TUD}}\label{applications_tud}
\end{subfigure}
\begin{subfigure}[t]{\figwidth}\centering
\censorbox{
\includegraphics[height=\figheight]{sources-applications-ultimaker-logo.png}
}
\caption{\censor{UM}}\label{applications_um}
\end{subfigure}
\begin{subfigure}[t]{\figwidth}\centering
\includegraphics[height=\figheight]{sources-applications-pinion-gear-motor.png}
\caption{Gear}\label{applications_gear}
\end{subfigure}
\begin{subfigure}[t]{\figwidth}\centering
\includegraphics[height=\figheight]{sources-applications-topopt-bone.png}
\caption{Bone}\label{applications_bone}
\end{subfigure}
\begin{subfigure}[t]{\figwidth}\centering
\includegraphics[height=\figheight]{sources-applications-gyroid.png}
\caption{Gyroid}\label{applications_gyroid}
\end{subfigure}
\begin{subfigure}[t]{\figwidth}\centering
\includegraphics[height=\figheight]{sources-applications-hex-grid.png}
\caption{Hex}\label{applications_hex}
\end{subfigure}
\begin{subfigure}[t]{.3\figwidth}
\includegraphics[height=\figheight]{sources-validation-widths-legend-small.pdf}
\end{subfigure}
\caption{
Visualization of the widths for the output toolpaths of the inward distributed beading scheme \revise{}{($N=3$) }applied to various example application objects.
From left to right and top to bottom: a house, a case for electronics, a statue, two common logos, a gear, a topologically optimized bone structure, a tilted homogeneous gyroid structure and a heterogeneous thickness hexagonal grid.
}
\label{applications_overview}
\end{figure*}

### 2020-01-20 1_intro.tex
lil edit because the paper in total is now only for FDM (reviewer 3.1)
add censoring (for reproduction in apendix of INRIA paper)

Our contributions are as follows:
\begin{itemize}
\item A geometric framework \revise{for generating densely filling contour-parallel toolpaths employing adaptive width, according to any beading scheme which decides on the bead spacing and widths.}{allowing various adaptive bead width control schemes used to generate contour-parallel toolpaths which minimize under- and overfill.}
\item A specific beading scheme for FDM printing which
\revise{}{furthermore} reduces the amount of \revise{deviation}{variation} in the extrusion widths compared to \revise{existing literature, }{the state of the art to be below a factor of 2.}
\revise{and which promotes smooth toolpaths that are equal to the preferred width toward the outline of the shape.}{}
\revise{}{
\item A back pressure compensation approach to accurately realize adaptive bead width on Bowden style hardware systems.
}
\end{itemize}

\revise{}{The presented framework is patented by Ultimaker and open source available at \url{github.com/Ultimaker/libArachne}.}

>>>>

Our contributions are as follows:
\begin{itemize}
\item A geometric framework \revise{for generating densely filling contour-parallel toolpaths employing adaptive width, according to any beading scheme which decides on the bead spacing and widths.}{allowing various adaptive bead width control schemes used to generate contour-parallel toolpaths which minimize under- and overfill.}
\item A specific beading scheme \revise{for FDM printing}{} which
\revise{}{furthermore} reduces the amount of \revise{deviation}{variation} in the extrusion widths compared to \revise{existing literature, }{the state of the art to be below a factor of 2.}
\revise{and which promotes smooth toolpaths that are equal to the preferred width toward the outline of the shape.}{}
\revise{}{
\item A back pressure compensation approach to accurately realize adaptive bead width on Bowden style hardware systems.
}
\end{itemize}

\revise{}{\xblackout{The presented framework is patented by Ultimaker and open source available at} \censor{\url{github.com/Ultimaker/libArachne}}.}

### 2020-01-20 6_2_printing_results.tex
add censoring (for reproduction in apendix of INRIA paper)

% discussion of print results
In \cref{print_naive} the underfill problem of the naive uniform offset approach is most prevalent for the Ultimaker word mark, which negatively impacts the visual quality and the stiffness of the part.
Moreover, in the case of the spatially graded honeycomb there are several fully disconnected hexagons, which means the object falls apart when picked up.
The honeycomb print is also missing all parts which are slightly more thin than the preferred bead width $w^*$.
\Cref{print_center} still shows some underfill, but considerably less than the uniform approach.
These prints also exhibit dark regions where the translucency of the layer is less because the bead is higher.
This can be explained by inaccuracies in the back pressure compensation method, which arise for bead widths which deviate from the preferred width by a large amount.
\Cref{print_inward} diminishes the underfill nearly completely and the visual quality of these prints is more homogenous than those of the other methods.
Moreover, the absence of dark regions signifies that our proposed method is more robust against inaccuracies in the deposition system.
However, both the centered and inward distributed approach introduce transitions to a different bead count in the word `Delft', which reduces the dimensional accuracy on the outline around those locations.

\begin{figure}
\centering
\setlength{\figwidth}{\columnwidth}
\begin{subfigure}{\figwidth}\centering
\includegraphics[width=\figwidth]{sources-applications-result-prints-target}
\caption{Outlines}\label{print_outlines}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[width=\figwidth]{sources-applications-result-prints-naive-bw.png}
\caption{Uniform}\label{print_naive}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[width=\figwidth]{sources-applications-result-prints-center-bw.png}
\caption{Centered}\label{print_center}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[width=\figwidth]{sources-applications-result-prints-inward-bw.png}
\caption{Inward distributed}\label{print_inward}
\end{subfigure}
\caption{
Test shapes printed using the uniform scheme, centered scheme and the inward distributed scheme.
The uniform technique produces distinct underfill areas.
The centered scheme shows some defects due to inaccurate control of extreme deposition widths.
The inward distributed scheme produces the least defects.
}
\label{prints}
\end{figure}

>>>>

% discussion of print results
In \cref{print_naive} the underfill problem of the naive uniform offset approach is most prevalent for \xblackout{the Ultimaker word mark}, which negatively impacts the visual quality and the stiffness of the part.
Moreover, in the case of the spatially graded honeycomb there are several fully disconnected hexagons, which means the object falls apart when picked up.
The honeycomb print is also missing all parts which are slightly more thin than the preferred bead width $w^*$.
\Cref{print_center} still shows some underfill, but considerably less than the uniform approach.
These prints also exhibit dark regions where the translucency of the layer is less because the bead is higher.
This can be explained by inaccuracies in the back pressure compensation method, which arise for bead widths which deviate from the preferred width by a large amount.
\Cref{print_inward} diminishes the underfill nearly completely and the visual quality of these prints is more homogenous than those of the other methods.
Moreover, the absence of dark regions signifies that our proposed method is more robust against inaccuracies in the deposition system.
However, both the centered and inward distributed approach introduce transitions to a different bead count in \xblackout{the word `Delft'}, which reduces the dimensional accuracy on the outline around those locations.

\begin{figure}
\centering
\setlength{\figwidth}{\columnwidth}
\begin{subfigure}{\figwidth}\centering
\censorbox{
\includegraphics[width=\figwidth]{sources-applications-result-prints-target}
}
\caption{Outlines}\label{print_outlines}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\censorbox{
\includegraphics[width=\figwidth]{sources-applications-result-prints-naive-bw.png}
}
\caption{Uniform}\label{print_naive}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\censorbox{
\includegraphics[width=\figwidth]{sources-applications-result-prints-center-bw.png}
}
\caption{Centered}\label{print_center}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\censorbox{
\includegraphics[width=\figwidth]{sources-applications-result-prints-inward-bw.png}
}
\caption{Inward distributed}\label{print_inward}
\end{subfigure}
\caption{
Test shapes printed using the uniform scheme, centered scheme and the inward distributed scheme.
The uniform technique produces distinct underfill areas.
The centered scheme shows some defects due to inaccurate control of extreme deposition widths.
The inward distributed scheme produces the least defects.
}
\label{prints}
\end{figure}
